What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-06 icpc/icpc2010.tex
multi label evaluation

Table \ref{tab:best-learn-per-tag} shows that MaxDB and MySQL have quite different results, the ROC values for reliability and functionality seem swapped between projects. It should be noted that for both projects Bayesian techniques did the best out of a wide variety of machine learners tested. Discriminative Multinomial Naive Bayes (DMNBtext), Naive Bayes (NaiveBayes) and Multinomial Naive Bayes (NaiveBayesMultinomal) are all based on Bayes theorem and all assume, naively, that the features are independent. The features we used are word counts per message. One beneficial aspect of this result is that it suggests we can have very fast training and classifying times since Naive Bayes can be calculated in $O(N)$ for $N$ features.
%http://nlp.stanford.edu/IR-book/html/htmledition/naive-bayes-text-classification-1.html

@@

We have presented the results of Mulan's multi-label learners in Table \ref{tab:mulan}.
Binary Relevance (BR), Calibrated Label Ranking (CLR) and Hierarchy Of Multilabel classifiERs (HOMER), performed the best. HOMER and BR acts as a hierarchy of learners, BR is flat while HOMER tries to build a deeper hierarchy in order to build a more accurate learner~\cite{mulan}. We feel that these classifiers performed better because they have the best micro and macro ROC scores than the other classifiers.

>>>>

Table \ref{tab:best-learn-per-tag} shows that MaxDB and MySQL have quite different results, the ROC values for reliability and functionality seem swapped between projects. It should be noted that for both projects Bayesian techniques did the best out of a wide variety of machine learners tested. Discriminative Multinomial Naive Bayes (DMNBtext), Naive Bayes (NaiveBayes) and Multinomial Naive Bayes (NaiveBayesMultinomal) are all based on Bayes theorem and all assume, naively, that the features are independent. The features we used are word counts per message. One beneficial aspect of this result is that it suggests we can have very fast training and classifying  since Naive Bayes can be calculated in $O(N)$ for $N$ features.
%http://nlp.stanford.edu/IR-book/html/htmledition/naive-bayes-text-classification-1.html

@@

We have presented the results of Mulan's multi-label learners in Table \ref{tab:mulan}.  Binary Relevance (BR), Calibrated Label Ranking (CLR) and Hierarchy Of Multilabel classifiERs (HOMER), performed the best. HOMER and BR acts as a hierarchy of learners, BR is flat while HOMER tries to build a deeper hierarchy in order to build a more accurate learner~\cite{mulan}. We feel that these classifiers performed better than other multilabel classifiers because they have the best micro and macro ROC scores than the other classifiers although their results seem comparable to the naive Bayesian learners we used in Section \ref{sec:suplabelling}.
